Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-16 ms.tex
A few more minor grammatical changes

To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}. 
We explore halo occupation distribution models (HOD) models in this work 
\citep[e.g.][]{seljak00,ma_fry00,scoccimarro01a,berlind02}, though other 
techniques that can be used to interpret such data, such as the conditional luminosity function 
\citep[CLF, e.g.,][]{yang03,vdBosch13}, exist. In this subsection, we review the ``standard" HOD 
model used in the present work, which assumes that there is no galaxy assembly bias. We refer to 
such a model as ``standard" because all HOD analyses of galaxy clustering to date have assumed no 
galaxy assembly bias. In the following subsection, we describe 
the Decorated HOD model described in \citet{hearin_etal16}. In both cases, we will only 
review the salient features of our methodology briefly; 
interested readers can always refer to {\tt halotools.readthedocs.io} and 
\citet{hearin_etal16} for further details.

@@

After populating a halo catalog with mock galaxies, we calculate the
comoving number density of our mock galaxy sample as $n_{\rm g} =
N_{\rm gal} / L_{\rm box}^3$, where $N_{\rm gal}$ is the total number of 
galaxies in the mock sample. We apply the distant-observer
approximation and use the simulation z-axis as the line-of-sight
direction, and the distance between points in the $xy$-plane to define
the projected distance $\rp.$ We place mock galaxies into
redshift-space by replacing each galaxy's $z$-coordinate with 
$z_{\rm RS} = z + V_{\rm z}/H_0.$ We count pairs of points in each of
our $\rp$ bins, rejecting pairs with $z_{\rm RS}-$ distance exceeding 
$\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection 
depth chosen by \citet{zehavi_etal11}. We employ the \citet{landyszalay93}
estimator to turn pair counts into a $\wprp$ prediction, as described
in detail in {\tt halotools.readthedocs.io}.

@@

We turn now to a discussion of our parameter inference analysis of projected galaxy clustering 
in Decorated HOD models that include a treatment of galaxy assembly bias. In this work, 
we consider only the simplest model of galaxy assembly bias, introducing only two new 
parameters, $A_{\rm cen}$ and $A_{\rm sat}$, that describe the strength of central galaxy 
and satellite galaxy assembly bias respectively. These parameters are limited to values 
of $-1 \le A_{\rm cen,sat} \le 1$, and $A_{\rm cen,sat}=0$ when there is no galaxy assembly bias. 
In this work, we use halo concentration as our secondary halo property, so $A_{\rm cen,sat}=1$ 
($A_{\rm cen,sat}=-1$) means that the mean number of galaxies per halo is maximally 
correlated (anti-correlated) with halo concentration. The model and its implementation 
in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above and 
in more detail in \citet{hearin_etal16}.

>>>>

To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}.
We explore halo occupation distribution models (HOD) models in this work
\citep[e.g.][]{seljak00,ma_fry00,scoccimarro01a,berlind02}, though other
techniques that can be used to interpret such data, such as the conditional luminosity function
\citep[CLF, e.g.,][]{yang03,vdBosch13}, exist. In this subsection, we review the ``standard" HOD
model used in the present work, which assumes that there is no galaxy assembly bias. We refer to
such a model as ``standard" because all HOD analyses of galaxy clustering to date have assumed no
galaxy assembly bias. In the following subsection, we describe
the Decorated HOD model described in \citet{hearin_etal16}. In both cases, we will only
review the salient features of our methodology briefly;
interested readers can always refer to {\tt http://halotools.readthedocs.io} and
\citet{hearin_etal16} for further details.

@@

After populating a halo catalog with mock galaxies, we calculate the
comoving number density of our mock galaxy sample as $n_{\rm g} =
N_{\rm gal} / L_{\rm box}^3$, where $N_{\rm gal}$ is the total number of
galaxies in the mock sample. We apply the distant-observer
approximation and use the simulation z-axis as the line-of-sight
direction, and the distance between points in the $xy$-plane to define
the projected distance $\rp.$ We place mock galaxies into
redshift-space by replacing each galaxy's $z$-coordinate with
$z_{\rm RS} = z + V_{\rm z}/H_0.$ We count pairs of points in each of
our $\rp$ bins, rejecting pairs with $z_{\rm RS}-$ distance exceeding
$\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection
depth chosen by \citet{zehavi_etal11}. We employ the \citet{landyszalay93}
estimator to turn pair counts into a $\wprp$ prediction, as described
in detail in {\tt http://halotools.readthedocs.io}.

@@

We turn now to a discussion of our parameter inference analysis of projected galaxy clustering
in Decorated HOD models that include a treatment of galaxy assembly bias. In this work,
we consider only the simplest model of galaxy assembly bias, introducing only two new
parameters, $A_{\rm cen}$ and $A_{\rm sat}$, that describe the strength of central galaxy
and satellite galaxy assembly bias respectively. These parameters are limited to values
of $-1 \le A_{\rm cen,sat} \le 1$, and $A_{\rm cen,sat}=0$ when there is no galaxy assembly bias.
In this work, we use halo concentration as our secondary halo property, so $A_{\rm cen,sat}=1$
($A_{\rm cen,sat}=-1$) means that the mean number of galaxies per halo is maximally
correlated (anti-correlated) with halo concentration. The model and its implementation
in {\tt Halotools} is discussed further in Section~\ref{subsection:decorated} above and
in more detail in \citet{hearin_etal16}.
